Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-29 manuscript/manuscript.Rmd
Code drop

We used the median shape of the combined experts' data as a baseline for all comparisons, as the "true" shape. To assess within-individual variation, we compared each worker's shape replicate to their own median shape. To assess within-group and between-group variation, we also compare those individual worker median shapes to the median shape of all other turkers and all other experts. We also measured the median absolute deviation (MAD) as a dispersion statistic for within-worker, within-group, and between-group comparisons.

To test whether turkers and experts were statistically distinguishable,

@@

```{r sum_table}
no_st <- fish_landmarks %>% filter(role != "student") %>% mutate(role = factor(role))

pcaed <- no_st %>% group_by(family, mark) %>% do(as_df(prcomp(cbind(.$x, .$y), scale=F, center=T)$x, role=as.character(.$role), ident=as.character(.$sha1mac))) %>% mutate(PC1 = as.numeric(PC1), PC2 = as.numeric(PC2))

meds <- pcaed %>% group_by(family, role, mark) %>% summarise(med=median(PC1)) %>% ungroup() %>% spread(role, med) %>% transmute(family, mark, value = log(abs(turker - morphologist)), stat="median")

mads <- pcaed %>% group_by(family, role, mark) %>% summarise(mad=mad(PC1)) %>% ungroup() %>% spread(role, mad) %>% transmute(family, mark, value = log(turker / morphologist), stat="mad")

all_stats <- bind_rows(meds, mads) %>% spread(stat, value)
```

@@

```{r median_tbl, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```

```{r turker_v_expert, anchor="figure"}
ggplot(all_stats, aes(median, mad, label=mark)) + geom_text() + labs(x="Accuracy", y="Precision")
```

@@

plot_tangent_space(coords, "PC1", "PC2")
```

@@

res <- plotTangentSpace(full_coords, groups=groups, axis1=1, axis2=2, verbose=T, warpgrids=F)$pc.scores

res <- as.data.frame(res)
res$id <- rownames(res)
res2<- res %>% separate(id, into=c("family", "name"), sep="\\|", extra="drop") %>% tbl_df()

p <- ggplot(res2, aes(x=PC1, y=PC2, col=family)) + geom_point() + theme(legend.position="none")

res2 %>% select(name, PC1) %>% write.table(file="lol.txt", quote=F, row.names=F, col.names=F, sep="\t")
```

```{r timing_plot, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received 6 minutes after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark."}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(res2))

@@

Using a median-expert time of `r as.character(morpho_per_image)` per image, we estimate that a single morphologist would take `r as.character(morpho_per_image * nrow(res2))` to landmark all `r nrow(res2)` images. At 5x replication, this would take `r as.character(morpho_per_image * nrow(res2) * 5)`. By comparison, turkers took a total of `r as.character(total_turker_time)` to complete all images at 5x replication.

@@

```{r turker_morph_procrustes_other_pc23, message=FALSE, warning=FALSE, fig.cap="PC2 and PC3 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC2", "PC3")
```

```{r turker_morph_procrustes_other_pc34, message=FALSE, warning=FALSE, fig.cap="PC3 and PC4 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC3", "PC4")
```

```{r turker_morph_procrustes_other_pc45, message=FALSE, warning=FALSE, fig.cap="PC4 and PC5 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC4", "PC5")
```

>>>>

We used the median shape of the combined experts' data as the "true" shape for all comparisons. To assess the accuracy of worker data, as compared

To assess the differences between turker and expert data, we compared the median turker position to the median expert position of each landmark. We assumed that the expert median was indeed the true position of that landmark, and calculated the absolute Euclidian distance. Larger distances would indicate low turker accuracy, while smaller distances would indicate high turker accuracy. We also examined the variance in turker landmarks. For each landmark, we rotated the cluster of points and took calculated the median absolute deviation between points along a single dimension. This

To assess within-individual variation, we compared each worker's shape replicate to their own median shape. To assess within-group and between-group variation, we also compare those individual worker median shapes to the median shape of all other turkers and all other experts. We also used the median absolute deviation (MAD) as a dispersion statistic for within-worker, within-group, and between-group comparisons. This is a statistic robust to outliers

@@

```{r turker_v_expert, fig.cap="Test figure caption", anchor="figure"}
no_st <- fish_landmarks %>% filter(role != "student") %>% mutate(role = factor(role))

tmp <- no_st %>% filter(family == "Aca", mark %in% c("A1", "A2"))

accuracy <- no_st %>% group_by(family, mark) %>% summarise(median = dist_2d(x, y, role)) %>% group_by(family) %>% mutate(outlier=upper_outlier(median, extreme = 2))

precision <- no_st %>% group_by(role, family, mark) %>% summarise(var = mad_2d(x, y)) %>% spread(role, var) %>% group_by(family, mark) %>% transmute(mad = log(turker / morphologist))

full_family <- data_frame(
  family=c("Aca", "Apo", "Bal", "Cha", "Gob", "Lab", "Pom", "Sco", "Tet"),
  full_family=c("Acanthuridae", "Apogonidae", "Balistidae", "Chaetodontidae", "Gobiidae", "Labridae", "Pomacentridae", "Scorpaenidae", "Tetraodontidae")
)

all_stats <- left_join(accuracy, precision) %>% left_join(full_family) %>% mutate(outlier_label = ifelse(outlier, as.character(mark), NA))

ggplot(all_stats, aes(median, mad, color=outlier)) + geom_point() + labs(x="Accuracy", y="Precision: log2 turker variance / expert variance ") + facet_wrap(~full_family)# + geom_dl(aes(label=outlier_label), size=1, list("top.bumptwice", dl.trans(y=y+0.1), cex=0.75)) + scale_color_manual(values=c("black", "red")) + ylim(-max(abs(all_stats$mad) + 0.25), max(abs(all_stats$mad) + 0.25)) + theme("legend.position" = "none")
```

@@

```{r median_tbl, eval=F, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, eval=F, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```

@@

plot_tangent_space(pca_df(coords), "PC1", "PC2")
```

@@

pcaed <- pca_df(full_coords) %>% separate(id, into=c("family", "name"), sep="\\|", extra="drop")

pcaed %>% select(name, PC1) %>% write.table(file="lol.txt", quote=F, row.names=F, col.names=F, sep="\t")

plot_tangent_space2(pcaed, labelmethod=list("chull.grid"))
```

```{r timing_plot, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received `r timing_data[[1, 'time']] %>% dminutes()` after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark."}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(no_st))

@@

Using a median-expert time of `r as.character(morpho_per_image)` per image, we estimate that a single morphologist would take `r as.character(morpho_per_image * nrow(no_st))` to landmark all `r nrow(no_st)` images. At 5x replication, this would take `r as.character(morpho_per_image * nrow(no_st) * 5)`. By comparison, turkers took a total of `r as.character(total_turker_time)` to complete all images at 5x replication.

@@

```{r turker_morph_procrustes_other_pc23, message=FALSE, warning=FALSE, fig.cap="PC2 and PC3 for turker / morphologist Procrustes space"}
coords_df <- pca_df(coords)
plot_tangent_space(coords_df, "PC2", "PC3")
```

```{r turker_morph_procrustes_other_pc34, message=FALSE, warning=FALSE, fig.cap="PC3 and PC4 for turker / morphologist Procrustes space"}
plot_tangent_space(coords_df, "PC3", "PC4")
```

```{r turker_morph_procrustes_other_pc45, message=FALSE, warning=FALSE, fig.cap="PC4 and PC5 for turker / morphologist Procrustes space"}
plot_tangent_space(coords_df, "PC4", "PC5")
```
